---
title: "RCDC-introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RCDC-introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(RCDC)
```

# Introduction

The **RCDC** package provides tools for robust community detection in
replicated noisy networks with node-level covariates. The main workflow models
the latent network, observation error rates, community memberships, and
covariate distributions jointly through an MCMC sampler.

The package implements:

1. `RobustCDC()`  
  The primary user-facing function. It fits a set of candidate community
  numbers and selects the final value of `K` using WAIC.

2. `robustCDC_MCMC()`  
  The fixed-`K` sampler used internally by `RobustCDC()`. This is useful for
  large-scale parallel workflows where each candidate `K` is run separately.

3. `robustCDC_MCMC_saveallparameters()`  
  A diagnostic version of the sampler that keeps full traces of latent
  networks and model parameters.

This vignette outlines the expected data format and the basic model-fitting
interface.

# Data Preparation

`RCDC` expects a three-dimensional array of replicated noisy adjacency
matrices:

```{r data-format, eval = FALSE}
dim(A_tilde)
# n x n x M
```

Rows and columns index nodes, and the third dimension indexes replicated noisy
network observations. Continuous node covariates can be passed through
`X_cont`, and categorical covariates can be passed through `X_cat`.

The hyperparameter list should contain prior settings for the network,
observation error, covariate, and mixing-proportion components:

```{r hyper, eval = FALSE}
hyper <- list(
  sigma = 10,
  a_alpha = 1,
  b_alpha = 1,
  a_beta = 1,
  b_beta = 1,
  mu0 = c(0, 0, 0),
  iota0 = c(1, 1, 1),
  a_tau = c(1, 1, 1),
  b_tau = c(0.01, 0.01, 0.01),
  F_cat = c(8),
  gamma0 = c(1),
  d = 1
)
```

# Running RCDC

Use `RobustCDC()` when you want the package to fit multiple candidate values of
`K` and select the model with the smallest WAIC:

```{r robustcdc-fit, eval = FALSE}
fit <- RobustCDC(
  A_tilde = A_tilde,
  X_cont = X_cont,
  X_cat = NULL,
  K = 5:30,
  n_iter = 2000,
  burn_in = 1000,
  hyper = hyper
)

fit
fit$z
fit$waic_table
```

# Fixed-K MCMC

For a single fixed value of `K`, call `robustCDC_MCMC()` directly:

```{r fixed-k, eval = FALSE}
fit_k <- robustCDC_MCMC(
  A_tilde = A_tilde,
  X_cont = X_cont,
  X_cat = NULL,
  K = 10,
  n_iter = 2000,
  burn_in = 1000,
  hyper = hyper
)
```

For large candidate grids, see the `parallel-runs` vignette for a template that
runs fixed-`K` jobs in parallel and combines WAIC values afterward.

# References

References will be added after the manuscript is available.
