---
title: "rcdc-introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rcdc-introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(rcdc)
```

# Introduction

The RCDC package provides tools for robust community detection in
multiple noisy observations of a latent true network with node-level covariates. The main workflow models
the latent network, observation error rates, community memberships, and
covariate distributions jointly through an MCMC sampler.

The package implements:

1. `RobustCDC()`  
  The primary user-facing function. It fits a set of candidate community
  numbers and selects the final value of `K` using WAIC.

2. `robustCDC_MCMC()`  
  The fixed-`K` sampler used internally by `RobustCDC()`. This is useful for
  large-scale parallel workflows where each candidate `K` is run separately.

3. `robustCDC_MCMC_saveallparameters()`  
  A diagnostic version of the sampler that keeps full traces of latent
  networks and model parameters.

This vignette outlines the expected data format and the basic model-fitting
interface.

# Simulation Setup

`RCDC` expects a three-dimensional array of noisy adjacency
matrices. Rows and columns index nodes, and the third dimension indexes
noisy observations of the same latent true network. Continuous node covariates can be passed
through `X_cont`, and categorical covariates can be passed through `X_cat`.

The following example simulates a three-community setting with four noisy
observations of a latent true network, three continuous covariates, and two
categorical covariates.

```{r simulation-setup, eval = FALSE}
library(rcdc)
library(aricode)

seed <- 123
set.seed(seed)

n <- 60
K0 <- 3
M <- 4
burn <- 200
niter <- 500

rho <- c(0.10, 0.30)
zeta <- c(1.0, 1.0)

hyper <- list(
  sigma = 10,
  a_alpha = 1,
  b_alpha = 1,
  a_beta = 1,
  b_beta = 1,
  mu0 = rep(0, K0),
  iota0 = rep(1, K0),
  a_tau = rep(1, K0),
  b_tau = rep(0.01, K0),
  F_cat = c(K0, K0),
  gamma0 = c(1, 1),
  d = 1
)

B <- matrix(-1.5, K0, K0)
diag(B) <- 0

mu <- diag(K0) - matrix(1 / K0, K0, K0)
mu <- mu * (10 / sqrt(2))

tau2 <- diag(3^2, K0)
theta <- rnorm(n, mean = zeta[1], sd = zeta[2])
alpha <- matrix(rho[1], K0, K0)
beta <- matrix(rho[2], K0, K0)
cat_rate <- c(0.7, 0.7)
```

The simulated data are generated with `dg()`:

```{r simulate-data, eval = FALSE}
sim <- dg(
  seed = seed,
  n = n,
  K = K0,
  M = M,
  p_cont = K0,
  p_cat = 2,
  F_s = K0,
  theta_true = theta,
  B = B,
  alpha = alpha,
  beta = beta,
  mu = mu,
  tau2 = tau2,
  correct_rate = cat_rate
)

z_true <- sim$truth$z
```

# Running RCDC

Use `RobustCDC()` to fit candidate values of `K` and select the model with the
smallest WAIC. The example below searches over `K = 2, ..., 5` and compares
the resulting labels with the known simulation truth using ARI and NMI.

```{r robustcdc-fit, eval = FALSE}
fit <- RobustCDC(
  A_tilde = sim$A_tilde,
  X_cont = sim$X_cont,
  X_cat = sim$X_cat,
  K = 2:5,
  n_iter = niter,
  burn_in = burn,
  hyper = hyper
)

print(fit)

z_hat <- fit$z
ARI_RCDC <- ARI(z_hat, z_true)
NMI_RCDC <- NMI(z_hat, z_true)
k_RCDC <- length(unique(z_hat))

ARI_RCDC
NMI_RCDC
k_RCDC
```

# Fixed-K MCMC

For a single fixed value of `K`, call `robustCDC_MCMC()` directly:

```{r fixed-k, eval = FALSE}
fit_k <- robustCDC_MCMC(
  A_tilde = sim$A_tilde,
  X_cont = sim$X_cont,
  X_cat = sim$X_cat,
  K = K0,
  n_iter = niter,
  burn_in = burn,
  hyper = hyper
)
```

For large candidate grids, see the `parallel-runs` vignette for a template that
runs fixed-`K` jobs in parallel and combines WAIC values afterward.

# References

References will be added after the manuscript is available.
