---
title: "RCDC-introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RCDC-introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(RCDC)
```

# Introduction

The **RCDC** package provides tools for robust community detection in
replicated noisy networks with node-level covariates. The main workflow models
the latent network, observation error rates, community memberships, and
covariate distributions jointly through an MCMC sampler.

The package implements:

1. `RobustCDC()`  
  The primary user-facing function. It fits a set of candidate community
  numbers and selects the final value of `K` using WAIC.

2. `robustCDC_MCMC()`  
  The fixed-`K` sampler used internally by `RobustCDC()`. This is useful for
  large-scale parallel workflows where each candidate `K` is run separately.

3. `robustCDC_MCMC_saveallparameters()`  
  A diagnostic version of the sampler that keeps full traces of latent
  networks and model parameters.

This vignette outlines the expected data format and the basic model-fitting
interface.

# Simulation Setup

`RCDC` expects a three-dimensional array of replicated noisy adjacency
matrices. Rows and columns index nodes, and the third dimension indexes
replicated noisy network observations. Continuous node covariates can be passed
through `X_cont`, and categorical covariates can be passed through `X_cat`.

The following example simulates an eight-community setting with four replicated
noisy networks, eight continuous covariates, and two categorical covariates.

```{r simulation-setup, eval = FALSE}
library(RCDC)
library(aricode)

seed <- 123
set.seed(seed)

n <- 200
k <- 8
M_local <- 4
burn_in <- 500
n_iter <- 1000

rho_combos <- c(0.10, 0.10)
zeta_combos <- list(c(1.0, 1.0))

hyper <- list(
  sigma = 10,
  a_alpha = 1,
  b_alpha = 1,
  a_beta = 1,
  b_beta = 1,
  mu0 = rep(0, 8),
  iota0 = rep(1, 8),
  a_tau = rep(1, 8),
  b_tau = rep(0.01, 8),
  F_cat = c(8, 8),
  gamma0 = c(1, 1),
  d = 1
)

B_strong <- matrix(-2, k, k)
diag(B_strong) <- 0

cat_rate_strong <- c(0.7, 0.7)

means_k8 <- diag(k) - matrix(1 / k, k, k)
means_k8 <- means_k8 * (10 / sqrt(2))

se_strong <- 3
tau2 <- diag(se_strong^2, 8)

theta_vector <- rnorm(
  n,
  mean = zeta_combos[[1]][1],
  sd = zeta_combos[[1]][2]
)
B_local <- B_strong
alpha_local <- matrix(rho_combos[1], k, k)
beta_local <- matrix(rho_combos[2], k, k)
cat_rate_local <- cat_rate_strong
tau2_local <- tau2
```

The simulated data are generated with `sim_data_new_thetainput()`:

```{r simulate-data, eval = FALSE}
sim <- sim_data_new_thetainput(
  seed = seed,
  n = n,
  K = k,
  M = M_local,
  p_cont = 8,
  p_cat = 2,
  F_s = 8,
  theta_true = theta_vector,
  B = B_local,
  alpha = alpha_local,
  beta = beta_local,
  mu = means_k8,
  tau2 = tau2_local,
  correct_rate = cat_rate_local
)

z_true <- sim$truth$z
```

# Running RCDC

Use `RobustCDC()` to fit candidate values of `K` and select the model with the
smallest WAIC. The example below searches over `K = 5, ..., 10` and compares
the resulting labels with the known simulation truth using ARI and NMI.

```{r robustcdc-fit, eval = FALSE}
RCDC <- RobustCDC(
  A_tilde = sim$A_tilde,
  X_cont = sim$X_cont,
  X_cat = sim$X_cat,
  K = 5:10,
  n_iter = n_iter,
  burn_in = burn_in,
  hyper = hyper
)

z_RCDC <- RCDC$z
ARI_RCDC <- ARI(z_RCDC, z_true)
NMI_RCDC <- NMI(z_RCDC, z_true)
k_RCDC <- length(unique(z_RCDC))

RCDC
ARI_RCDC
NMI_RCDC
k_RCDC
```

# Fixed-K MCMC

For a single fixed value of `K`, call `robustCDC_MCMC()` directly:

```{r fixed-k, eval = FALSE}
fit_k <- robustCDC_MCMC(
  A_tilde = sim$A_tilde,
  X_cont = sim$X_cont,
  X_cat = sim$X_cat,
  K = 10,
  n_iter = n_iter,
  burn_in = burn_in,
  hyper = hyper
)
```

For large candidate grids, see the `parallel-runs` vignette for a template that
runs fixed-`K` jobs in parallel and combines WAIC values afterward.

# References

References will be added after the manuscript is available.
